Metric-learn: Metric Learning in Python

### 2019-07-17 metric-learn-jmlr.tex
wip

\usepackage{jmlr2e}
\usepackage{minted}
\usepackage[colorinlistoftodos]{todonotes}

@@

\texttt{metric-learn} contains most of the highly cited Mahalanobis metric learning algorithms. Here is a list of the algorithms contained in \texttt{metric-learn}:
\begin{itemize}
    \item Supervised Metric Learning algorithms: 
    Supervised algorithms learns a metric that brings closer together points from the same class and spreads further away points from a different class.
    \begin{itemize}
        \item NCA: Neighborhood Components Analysis
        \item LMNN: Large Margin Nearest Neighbors
        \item RCA: Relative Components Analysis
        \item LFDA: Local Fisher Discriminant Analysis
    \end{itemize}
    \item Weakly Supervised Metric Learning algorithms:
    Weakly Supervised algorithms use less information than the previous algorihtms: they only take tuple of points and possibly a corresponding label. See below for more concrete examples of algorithms learning on tuples.
    \begin{itemize}
        \item Pairs Learners: 
        Pairs learners take as input pair of points, and a corresponding label indicating whether the two points are similar or not. They will learn a metric that brings points from a similar pair closer together, and points from a dissimilar pair further away from each other.
        \begin{itemize}
            \item MMC: Mahalanobis Metric for Clustering
            \item SDML: Sparse High-Dimensional Metric Learning (SDML)
            \item ITML: Information Theoretic Metric Learning (ITML)
        \end{itemize}
        \item Quadruplets Learners: 
        Quadruplets learners take as input quadruplets of points. They learn a metric that brings the two first points of each quadruplet closer than the two last points are.
        \begin{itemize}
            \item LSML: Metric Learning from Relative Comparisons by Minimizing Squared Residual
        \end{itemize}
    \end{itemize}
\end{itemize}

>>>>

\usepackage{jmlr2e}
\usepackage{minted}
\usepackage[demo]{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[colorinlistoftodos]{todonotes}

@@

\texttt{metric-learn} contains most of the highly cited Mahalanobis metric learning algorithms.

\subsection{Mahalanobis metric learning}
Mahalanobis learning algorithms learn a

Here is a list of the algorithms contained in \texttt{metric-learn}:
\subsection{Supervised Metric Learning algorithms}
Supervised algorithms learns a metric that brings closer together points from the same class and spreads further away points from a different class.
\begin{itemize}
    \item NCA: Neighborhood Components Analysis
    \item LMNN: Large Margin Nearest Neighbors
    \item RCA: Relative Components Analysis
    \item LFDA: Local Fisher Discriminant Analysis
\end{itemize}
\subsection{Weakly Supervised Metric Learning algorithms}
Weakly Supervised algorithms use less information than the previous algorihtms: they only take tuple of points and possibly a corresponding label. See below for more concrete examples of algorithms learning on tuples.
    \subsubsection{Pairs Learners} 
    Pairs learners take as input pair of points, and a corresponding label indicating whether the two points are similar or not. They will learn a metric that brings points from a similar pair closer together, and points from a dissimilar pair further away from each other.
    \begin{itemize}
        \item MMC: Mahalanobis Metric for Clustering
        \item SDML: Sparse High-Dimensional Metric Learning (SDML)
        \item ITML: Information Theoretic Metric Learning (ITML)
    \end{itemize}

    \begin{figure}[H]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{pairs_without_metric.png}
  \caption{Original points, before metric learning}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{pairs_with_metric.png}
  \caption{Points after metric learning (ITML)}
  \label{fig:sub2}
\end{subfigure}
\caption{Metric learning with pairwise constraints}
\label{fig:test}
\end{figure}

    \subsubsection{Quadruplets Learners}
    Quadruplets learners take as input quadruplets of points. They learn a metric that brings the two first points of each quadruplet closer than the two last points are.
    \begin{itemize}
        \item LSML: Metric Learning from Relative Comparisons by Minimizing Squared Residual
    \end{itemize}
